Best Practices for Alchemical Free Energy Calculations: v\versionnumber

### 2020-01-14 paper/manuscript.tex
corrected columning for the checklist

\section{Conclusions}
\todo[inline, color={green!20}]{ASJSM:Write conclusions}
%              Terminology                  %
\section{Terminology and abbreviations}
\label{sec:tem-abbrev}
\item Feature Box covering major technical terms and abbreviations
\item Examples:
\item EXP, BAR, MBAR
\item Double decoupling, single-topology, dual-topology, hybrid-topology, coupled-topology
\item FEP (free energy perturbation), alchemical, AFE (alchemical free energy)
\todo[inline]{JS: should this be combined with the acronyms section at the beginning of the paper?}
%                Software                    %
\section{Available software -- a summary}
\todo[inline]{ASJSM: Expand and add more references. }
\label{sec:software}
There are several softwares availble for carrying out alchemical free energy calculations. In this section we discuss some of the popular commercial and free tools along with their features. 
\item Commercial:
    \item FEP+ is a tool offered by Schr\"{o}dinger Inc. under a commercial license. It has an intuitive GUI which makes it easier for non-experts to run alchemical free energy calculations and analyze the results. It runs DESMOND MD package under the hood and hence parallelizes very well on the GPUs. 
    \item Flare is a commercial structure-based drug design software offered by Cresset. Similar to FEP+ it has an easily accessible user interface and strives to facilitate free energy calculations for non-experts while offering advanced users full control via a Python API. It only runs on GPUs, using CUDA or OpenCL.
    \item The molecular operating environment (MOE) offered by the Chemical Computing Group (CCG) has a tool for performing free energy calculations. It is build on AMBER-TI (cf. below).
\item Free or low-cost for academics / commercial for industry:
	\item CHARMM has a variety of tools developed over the years. PERT module can be used to define initial and final states and define the intermediate lambda points. FREN and BAR modules can be used to analyze the data after the MD run. Lambda-dynamics based free energy calulation can be carried out using the BLOCK module.  
	\item TIES and AMBER FEW? (Peter Coveney)
	\item AMBER, including its new pmemd.cuda version support free energy calculation. 
\item Free (libre) open source:
	\item PLUMED is an open source tool which enables the usage of a variety of MD engines. It is designed as a plugin for MD packages such that it analyzes the trajectory on the fly. It also offers a VMD based plugin for the computation of collective variables.   	
	\item SIRE  is a free, open source, multiscale molecular simulation framework, written to allow computational modellers to quickly prototype and develop new algorithms for molecular simulation and molecular design. 
	\item YANK is a tool developed by John Chodera and group on the top of OpenMM MD package. It allows the users to write their inputs in easy-to-use YAML format.
	\item GROMACS is a molecular simulation package with a significant number of free energy methods implementations. The LiveCOMS GROMACS tutorial has an example free energy calculation~\cite{lemkul2018From}.
	\item pmx for mutations
\item Setup tools
	\item FESetup: AMBER, gromacs, Sire
	\item Lomap/Lomap2 : Relative alchemical transformation graph planning
	\item CHARMM-GUI is a web based tool for setting up a variety of MD simulations. It can be used to generate CHARMM scripts for solvation and ligand-binding free energy calculations.
\item Analysis tools:
	\item Free Energy Workflows: Sire-specific free energy map analysis using weighted path averages
	\url{https://github.com/michellab/freenrgworkflows}
	\item Alchemlyb: Multipackage free energy analysis
	\url{https://github.com/alchemistry/alchemlyb}
	\item pymbar: MBAR implementation, but have to roll your own analysis wrapper
	\url{https://github.com/choderalab/pymbar}

@@

\newpage
\section{Checklist}
\label{sec:checklist}
\todo[inline, color={green!20}]{JS: @everyone Please input your own suggestions, I made some points off the top of my head. Feel free to add helpful citations to any of the bullet points}
\todo[inline, color={green!20}]{JS: @self,ASJSM do some final formatting when text is complete.}
%Checklist:
%%%%%%%%%%%%%%%% 
%% Checklist-specific precommands:
\newenvironment{checklist_font}{\fontfamily{lmss}\small\selectfont}{\par}
\newlist{todolist}{itemize}{2}
\setlist[todolist]{label=$\square$}
%% start checklist:
\begin{checklist_font}
\begin{itemize}
\begin{todolist}

@@

%%%%%%%%%%%%%%%% 
% end checklist:
\end{todolist}
\end{itemize}
\end{checklist_font}
%%%%%%%%%%%%%%%%%
% This provides a checklist which
% - spans a full page
% - consists of multiple sub-checklists
% - exists on a separate page
% This style of checklist will be especially helpful if you want to encourage readers to print and use your checklist in practice, as they
% can easily print it without also printing other material from your manuscript. However, other styles of checklist are also possible (below).
% \begin{Checklists*}[p!]

>>>>

\section{Conclusions}
\todo[inline, color={green!20}]{ASJSM:Write conclusions}
Alchemical free energy calculations have seen a vast increase in popularity also in the pharmaceutical industry for structure based drug discovery~\cite{schind}. Commercial products such as FEP+ and Flare,

%%%%%%%%%%%%%%%%%%%%
%                Software                    %
%%%%%%%%%%%%%%%%%%%%
\section{Available software -- a summary}
\todo[inline]{ASJSM: Expand and add more references. }
\label{sec:software}
There are several softwares availble for carrying out alchemical free energy calculations. In this section we discuss some of the popular commercial and free tools along with their features. 
\begin{itemize}
\item Commercial:
   \begin{itemize}
    \item FEP+ is a tool offered by Schr\"{o}dinger Inc. under a commercial license. It has an intuitive GUI which makes it easier for non-experts to run alchemical free energy calculations and analyze the results. It runs DESMOND MD package under the hood and hence parallelizes very well on the GPUs. 
    \item Flare is a commercial structure-based drug design software offered by Cresset. Similar to FEP+ it has an easily accessible user interface and strives to facilitate free energy calculations for non-experts while offering advanced users full control via a Python API. It only runs on GPUs, using CUDA or OpenCL.
    \item The molecular operating environment (MOE) offered by the Chemical Computing Group (CCG) has a tool for performing free energy calculations. It is build on AMBER-TI (cf. below).
    \end{itemize}
\item Free or low-cost for academics / commercial for industry:
	\begin{itemize}
	\item CHARMM has a variety of tools developed over the years. PERT module can be used to define initial and final states and define the intermediate lambda points. FREN and BAR modules can be used to analyze the data after the MD run. Lambda-dynamics based free energy calulation can be carried out using the BLOCK module.  
	\item TIES and AMBER FEW? (Peter Coveney)
	\item AMBER, including its new pmemd.cuda version support free energy calculation. 
	\end{itemize}
\item Free (libre) open source:
	\begin{itemize}
	\item PLUMED is an open source tool which enables the usage of a variety of MD engines. It is designed as a plugin for MD packages such that it analyzes the trajectory on the fly. It also offers a VMD based plugin for the computation of collective variables.   	
	\item SIRE  is a free, open source, multiscale molecular simulation framework, written to allow computational modellers to quickly prototype and develop new algorithms for molecular simulation and molecular design. 
	\item YANK is a tool developed by John Chodera and group on the top of OpenMM MD package. It allows the users to write their inputs in easy-to-use YAML format.
	\item GROMACS is a molecular simulation package with a significant number of free energy methods implementations. The LiveCOMS GROMACS tutorial has an example free energy calculation~\cite{lemkul2018From}.
	\item pmx for mutations
	\end{itemize}
\item Setup tools
	\begin{itemize}
	\item FESetup: AMBER, gromacs, Sire
	\item Lomap/Lomap2 : Relative alchemical transformation graph planning
	\item CHARMM-GUI is a web based tool for setting up a variety of MD simulations. It can be used to generate CHARMM scripts for solvation and ligand-binding free energy calculations.
	\end{itemize}
\item Analysis tools:
	\begin{itemize}
	\item Free Energy Workflows: Sire-specific free energy map analysis using weighted path averages
	\url{https://github.com/michellab/freenrgworkflows}
	\item Alchemlyb: Multipackage free energy analysis
	\url{https://github.com/alchemistry/alchemlyb}
	\item pymbar: MBAR implementation, but have to roll your own analysis wrapper
	\url{https://github.com/choderalab/pymbar}
	\end{itemize}
\end{itemize}

@@

\section{Checklist}
\label{sec:checklist}
\todo[inline, color={green!20}]{JS: @everyone Please input your own suggestions, I made some points off the top of my head. Feel free to add helpful citations to any of the bullet points}
\todo[inline, color={green!20}]{JS: @self,ASJSM do some final formatting when text is complete.}
\onecolumn
%Checklist:
%%%%%%%%%%%%%%%% 
%% Checklist-specific precommands:
\newenvironment{checklist_font}{\fontfamily{lmss}\small\selectfont}{\par}
\newlist{todolist}{itemize}{2}
\setlist[todolist]{label=$\square$}
%% start checklist:
\begin{checklist_font}
\begin{itemize}
\begin{todolist}

@@

%%%%%%%%%%%%%%%% 
% end checklist:
\end{todolist}
\end{itemize}
\end{checklist_font}
%%%%%%%%%%%%%%%%%
\twocolumn
% This provides a checklist which
% - spans a full page
% - consists of multiple sub-checklists
% - exists on a separate page
% This style of checklist will be especially helpful if you want to encourage readers to print and use your checklist in practice, as they
% can easily print it without also printing other material from your manuscript. However, other styles of checklist are also possible (below).
% \begin{Checklists*}[p!]
